**Evalution of binary classification pipelines and methods for 16S rRNA gene data**

### 2018-11-14 submission/manuscript.Rmd
add cvAUCs for HP

######################################################################
#------------ Load .tsv data generated in Python -----------------#
######################################################################

@@

######################################################################
#------------ Put all the loaded AUC tables together -----------------#
######################################################################
all <- bind_rows(logit, l1svm, l2svm, svmRBF, xgboost, rf, dt) %>% 
  group_by(model)
```

>>>>

######################################################################
#---Load .tsv data with CV and test AUC data generated in Python ----#
######################################################################

@@

######################################################################
#------------ Put all the loaded AUC tables together -----------------#
######################################################################
all <- bind_rows(logit, l1svm, l2svm, svmRBF, xgboost, rf, dt) %>% 
  group_by(model)

######################################################################
#---Load .tsv data with cvAUCs for hyper-parameters  ----#
######################################################################
# Read in hyper-parameter AUCs generated from L2 logistic regression model for all samples:
logit <- read.delim('../data/process/L2_Logistic_Regression_parameters.tsv', header=T, sep='\t')%>%
  select(-X) %>% 
  mutate(meanAUC=rowMeans(.[, 2:101])) %>% 
  select(C, meanAUC) 
# Read in hyper-parameter AUCs generated from L1 Linear SVM model for all samples:
l1svm <- read.delim('data/process/L1_SVM_Linear_Kernel_parameters.tsv', header=T, sep='\t')%>%
  select(-X) %>% 
  mutate(meanAUC=rowMeans(.[, 2:101])) %>% 
  select(C, meanAUC) 
# Read in hyper-parameter AUCs generated from L2 Linear SVM model for all samples:
l2svm <- read.delim('data/process/L2_SVM_Linear_Kernel_parameters.tsv', header=T, sep='\t')%>%
  select(-X) %>% 
  mutate(meanAUC=rowMeans(.[, 2:101])) %>% 
  select(C, meanAUC)

```
